Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
review DSVerifier Verification Flow

The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it i.e.} stability)
is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
If any property violation is found, DSVerifier reports a
counterexample, which contains system inputs or parametric deviations
$\Delta{G}$ that lead the system to a failure.  A successful verification
result is reported if the system is safe with respect to $\phi$.  In
particular, the stability verification is complete and sound, since it does
not depend on system inputs and outputs.
In the case of stability, the specification $\phi$ consists in a number of assumptions
on the polynomial coefficients following Jury's Criteria, as well as the restrictions
set in the representation of these coefficients by the function $f$ [eq. \ref{FWL_tf}].

>>>>

The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it i.e.}, robust stability)
is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
If any property violation is found, then DSVerifier reports a
counterexample, which contains system inputs or parametric deviations
$\Delta{G}$ that lead the system to a failure.  A successful verification
result is reported if the system is safe with respect to $\phi$.  In
particular, the stability verification is complete and sound, since it does
not depend on system inputs and outputs.
In the case of stability, the specification $\phi$ consists in a number of assumptions
on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
set in the representation of these coefficients by the function $f$ (Eq. \ref{FWL_tf}).
